---
title: "EDA ON INDIAN TRADE OF 2021-22 & 2022-23"
author: "Saikat Kumar Ghosh"
date: "2023-11-05"
output:
  pdf_document: default
  html_document: default
---

Loading the libraries.

```{r}
library(readxl)
library(ggplot2)
library(ggpubr)
```

This data has been taken from Indian government's Ministry of Commerce's website.

The data has Country wise ,Commodity wise all information of Export & Import of last two years.

Primary Objectives of this EDA:

1.To be able to tell about India's Export vs Import percentage of last two financial years.

2.Top trading partners of India.

3.Export vs Import percentage with other countries of last two years.

4.Top Commodities which India exports in other countries.

5.Top commodities which India imports from other countries.

6.Top 15 High Growth Export Commodities .

7.Top 15 High Growth Import Commodities.

Importing the data and Cleaning it.

```{r}
#Importing the excel file of trade data of all countries with india.
trade_data<-read_excel("E:/Learning_related/R_codes/R_During_Msc/EDA/EDA_DATA_Main.xlsx",sheet = "AllCountrywiseTrade")
#View(trade_data)
print(trade_data)
#Replacing NA values with 0.Here we have taken only the columns with numeric values otherwise it will through error .
#Here trade_data[3:6] creates a data.frame taking 3rd to 6th column and within that we replace NA values with zeros.
trade_data[3:6][is.na(trade_data[3:6])]<-0.00

#View(trade_data)

#Creating two new columns under the name Total_trade(2021-2022) &Total_trade(2022-2023)
`Total_trade(2021-2022)`<-trade_data$`Export(2021-2022)`+trade_data$`Import(2021-2022)`
`Total_trade(2022-2023)`<-trade_data$`Export(2022-2023)`+trade_data$`Import(2022-2023)`
`Trade_Growth`<-((`Total_trade(2022-2023)`-`Total_trade(2021-2022)`)/`Total_trade(2021-2022)`)*100

#Adding new column under the name Total_trade & Trade_Balance for both years.
trade_data<-cbind(trade_data,`Total_trade(2021-2022)`,`Total_trade(2022-2023)`,`Trade_Growth`)
trade_data$Trade_Growth[is.na(trade_data$Trade_Growth)|is.infinite(trade_data$Trade_Growth)]<-0.00

View(trade_data)


#Sorting the data in descending order of Total_trade(2021-2022) 
sorted_data21.22<-trade_data[rev(order(trade_data$`Total_trade(2021-2022)`)),]

#Sorting the data in descending order of Total_trade(2022-2023).Order() by deafult returns indices as per ascending order.
sorted_data22.23<-trade_data[rev(order(trade_data$`Total_trade(2022-2023)`)),]
#Creating a new table of top10 trading partners based on the Total_trade column.
`Top.10.trading.parteners(2021-2022)`<-sorted_data21.22[1:10,]
#Creating new data.frame of top10 trading partners based on the Total_trade column.
`Top.10.trading.parteners(2022-2023)`<-sorted_data22.23[1:10,]

#Sorting the Countries wrt total trade growth .
sorted_on.Trade_growth<-trade_data[rev(order(trade_data$`Trade_Growth`)),]
Top10.countries.trade_growth<-sorted_on.Trade_growth[1:10,]

#View(Top10.countries.trade_growth)

#Commodity wise export Data.
commodity_export<-read_excel("E:/Learning_related/R_codes/R_During_Msc/EDA/EDA_DATA_Main.xlsx",sheet = "CommoditywiseExport")

View(commodity_export)
#Commodity wise import Data.
commodity_import<-read_excel("E:/Learning_related/R_codes/R_During_Msc/EDA/EDA_DATA_Main.xlsx",sheet = "CommoditywiseImport")

View(commodity_import)

```

Year wise total export import comparison:

Few Terms:

Trade Balance: Total Export-Total Import.(Negative Trade Balance means the country has trade deficit)

Trade Deficit:Total Import- Total Export.

When Trade Balance is positive it is called Trade Surplus whereas for negative Trade Balance it is called Trade Deficit.

As we can see that India's Import percentage of last two years is 59.24% & 61.3% respectively,whereas the Export percentage is:40.76% & 38.7% of total trade.

So clearly India has Trade Deficit of 18.48% for FY2021-22 & Trade Deficit of 22.6% for FY2022-23.

Moreover we can see that in Fy2022-23 India's trade deificit has increased by 22.28 % compared to Fy2021-22.

```{r}
#Yearwise total expott import comparison.
#Pie chart for 2021-22 data.
slices.1<-c(sum(trade_data$`Export(2021-2022)`),sum(trade_data$`Import(2021-2022)`))
lbls.1<-c("Export","Import")
pct.1<-round(slices.1/sum(slices.1)*100,digits = 2)
lbls.1<-paste(lbls.1,pct.1)
#adding percentage to the labels.
lbls.1<-paste(lbls.1,"%",sep = "")

FY.2021.22_pie<-pie(slices.1,labels=lbls.1,col=rainbow(length(slices.1)),
    main = "Pie chart of Total Trade of FY2021-22")

slices.2<-c(sum(trade_data$`Export(2022-2023)`),sum(trade_data$`Import(2022-2023)`))
lbls.2<-c("Export","Import")
pct.2<-round(slices.2/sum(slices.2)*100,digits = 2)
lbls.2<-paste(lbls.2,pct.2)
#adding percentage to the labels.
lbls.2<-paste(lbls.2,"%",sep = "")

FY.2022.23_pie<-pie(slices.2,labels=lbls.2,col=rainbow(length(slices.2)),
    main = "Pie chart of Total Trade of FY2022-23")

par(mfrow=c(1,2),mar = c(4, 4, 2, 1))
pie(slices.1,labels=lbls.1,col=rainbow(length(slices.1)),
    main = "Total Trade of FY2021-22")
pie(slices.2,labels=lbls.2,col=rainbow(length(slices.2)),
    main = "Total Trade of FY2022-23")
#FY.2021.22_pie
#FY.2022.23_pie
#grid.arrange(FY.2021.22_pie,FY.2022.23_pie,ncol=2)
```

Year wise top 10 trading partners:

1.Here we can see that USA,China & UAE holds the top spot when it comes to trade with india.

2.As we can see from the graph that Russia was not the the top 10 list in FY2021-22.But it holds the 5th spot in top trading partners in FY2022-23.

Note:During Russia Ukraine war when UN imposed sactions on Russia ,India imported crude oil at heavy discounts from Russia .

```{r}

FY2021_22<-ggplot(`Top.10.trading.parteners(2021-2022)`,aes(x=reorder(Country,-`Total_trade(2021-2022)`),y=`Total_trade(2021-2022)`/1000,fill=Country))+
  geom_bar(stat="identity")+
  ylim(0,130)+
  labs(x="Country",
  y="Total trade in USD billion",
  title = "Top 10 trading partners of India",
  subtitle ="FY2021_22")+
  scale_fill_manual(values = c( "green", "blue", "orange", "purple", "pink","brown", "cyan", "yellow","magenta", "gold"))+
  theme(legend.position = "none",axis.text.x= element_text(angle = 45, hjust = 1, size = 8))
  
  
#reorder(xaxis_column,-yaxis_column) has been used to reorder the bar graphs in descending order of height of the bars.
#For ascending order change '-' sigh into '+'
#Syntax for using reorder:ggplot(dataframe name, aes(x=reorder(column1,±column2),y=column2)

FY2022_23<-ggplot(`Top.10.trading.parteners(2022-2023)`,aes(x=reorder(Country,-`Total_trade(2022-2023)`),y=`Total_trade(2022-2023)`/1000,fill=Country))+
  geom_bar(stat="identity")+
  ylim(0,130)+
  labs(x="Country",
       y="Total trade in USD billion",
       title = "Top 10 trading partners of India",
       subtitle="FY2022_23")+
  scale_fill_manual(values = c("blue", "orange", "purple", "pink","brown","red", "cyan", "yellow","magenta", "gold"))+
  theme(legend.position = "none",axis.text.x= element_text(angle = 45, hjust = 1, size = 8))
  
print(FY2022_23)
print(FY2021_22)

ggarrange(FY2021_22,FY2022_23,ncol = 2)

#Growth plot of these top 10 trading partners.
Growth_plt<-ggplot(`Top.10.trading.parteners(2022-2023)`,aes(x=reorder(Country,-Trade_Growth),y=Trade_Growth,fill=Country))+
  geom_bar(stat = "identity")+
  labs(y="%Growth",
       x="Country",
       title = "Percentage of Growth in Trade with India")+
  theme(legend.position = "none",axis.text.x= element_text(angle = 45, hjust = 1, size = 8,face = "bold"))+
  geom_text(aes(label=round(Trade_Growth,digits = 2)),vjust=-1,size=3)
print(Growth_plt)
```

In the last graph we see trade growth of Russia with India is the highest (a staggering 276.08 percentage of increase in Trade relation with india.Reason:Russia Ukraine War,Sanctions on Russia by UN and import of Crude Oil from Russia at heavy discounted prices.

Country wise export import comparison of 2021-22:

From the plot below we can clearly see that India has negative Trade Balance for most of its trading partners other than USA.

For Iraq ,China & Saudi Arab the trade deficit is highest,for Singapore,UAE &Hong Kong it is moderately on the positive side whereas only for USA India has negative trade deficit.

Note: No matter what people say the data clearly shows that India is highly dependent on Chinese products.

```{r}
#2021-22 Country wise export import comparison.

# Extract the data
export.data<- `Top.10.trading.parteners(2021-2022)`$`Export(2021-2022)`
import.data<- `Top.10.trading.parteners(2021-2022)`$`Import(2021-2022)`
countries <- `Top.10.trading.parteners(2021-2022)`$Country
data2021_22<-data.frame(countries,export.data,import.data)

#View(data2021_22)


#Reshaping the data manually without any external function to plot the data in multiple bar diagram.
reshaped_data2021_22<-data.frame(
  Country=rep(countries,each=2),
  Trade_Type=rep(c("Export","Import"),10),
  values=c(76167.01, 43314.07,21259.79, 94570.57,28044.88, 44833.48,8758.94, 34100.58,
           2403.27, 31927.05,11150.61, 18962.19,10984.80, 19096.61,8471.51, 17702.83,
           8085.03, 17477.20,8283.13, 16756.17)
)

#View(reshaped_data2021_22)

#Multiple bar diagram.
export_import_comparison.2021.22_1<-ggplot(reshaped_data2021_22,aes(x=Country,y=values,fill=Trade_Type))+
  geom_bar(stat="identity",position = "dodge")+
  ylim(0,100000)+
  labs(y="USD million",
       title = "Export Import Comparison of Fy2021-22",
       fill="Trade Type")+
  theme(axis.text.x =element_text(angle = 90,size=5) )

print(export_import_comparison.2021.22_1)

#stack diagram with same level.
export_import_comparison.2021.22_2<-ggplot(reshaped_data2021_22,aes(x=Country,y=values,fill=Trade_Type))+
  geom_bar(stat="identity",position = "fill")+
  labs(y="Total Trade",
       title = "Export Import Comparison of Fy2021-22",
       fill="Trade Type")+
  theme(axis.text.x =element_text(angle = 90,size=5) )

print(export_import_comparison.2021.22_2)

```

Country wise export import comparison of 2022-23 :

Here we can see that India has negative Trade Balance for most of its top trading partners other than USA.

```{r}
#2022-23 export import comparison.

export.data <- `Top.10.trading.parteners(2022-2023)`$`Export(2022-2023)`
import.data <- `Top.10.trading.parteners(2022-2023)`$`Import(2022-2023)`
countries <- `Top.10.trading.parteners(2022-2023)`$Country
data2022_23<-data.frame(countries,export.data,import.data)

#View(data2022_23)

reshaped_data2022_23<-data.frame(
  Country=rep(countries,each=2),
  Trade_Type=rep(c("Export","Import"),10),
  values=c(78542.74, 50240.10,15306.10, 98505.79,31608.79, 53231.66,10727.65, 42035.27,3146.95, 46212.71,
           10024.30, 28820.41,2696.72, 34385.50,11992.94, 23595.35,9892.61, 18274.95,
           6654.10, 21227.32)
)

#View(reshaped_data2022_23)

#Multiple bar diagram.
export_import_comparison.2022.23_1<-ggplot(reshaped_data2022_23,aes(x=Country,y=values,fill=Trade_Type))+
  geom_bar(stat="identity",position = "dodge")+
  labs(y="USD million",
       title = "Export Import Comparison of Fy2022-23",
       fill="Trade Type")+
  theme(axis.text.x =element_text(angle = 90,size=5))

print(export_import_comparison.2022.23_1)

#stack diagram with same level.
export_import_comparison.2022.23_2<-ggplot(reshaped_data2022_23,aes(x=Country,y=values,fill=Trade_Type))+
  geom_bar(stat="identity",position = "fill")+
  labs(y="Total Trade",
       title = "Export Import Comparison of Fy2022-23",
       fill="Trade Type")+
  theme(axis.text.x =element_text(angle = 90,size=5))

print(export_import_comparison.2022.23_2)

#Multiple plot in same page of export_import_comparison.2021.22_1,export_import_comparison.2022.23_1
ggarrange(export_import_comparison.2021.22_1,export_import_comparison.2022.23_1,ncol=2)

#Multiple plot in same page of export_import_comparison.2021.22_2,export_import_comparison.2022.23_2
ggarrange(export_import_comparison.2021.22_2,export_import_comparison.2022.23_2,ncol = 2)
```

From the stacked bar diagram we can see that in in FY2021-22 for Iraq,China & Saudi Arab the percentage of trade deficit is the highest,for Singapore &UAE it is moderately high whereas for USA India has trade surplus.

In FY2022-23 for Russia,Iraq & China the percentage of trade deficit is highest,for Singapore,UAE & Hong Kong it is moderately high whereas only for USA India has trade surplus.

Commodity wise Export analysis:

From this plot we can see that top 10 Exported commodities of both FY2021-22 &FY2022-23 where Mineral fuel,Natural /Cultured pearls and Nuclear Reactor and mechanical appliances holds the top 3 spot in FY2021-22 and Mineral fuel,Natural /Cultured pearls and Electrical equipments &appliances (Ex:TV ,Sound Recorders etc.) holds the top spot in FY2022-23.

```{r}
#Project Goods:LABORATORY CHEMICALS,CREWS BAGGAGE
#Miscelleneous Goods:description not given clearly
#Commoditywise Export analysis.

#View(commodity_export)

#sorted based on 2021-22 india's commodity export.
sorted_export_data21.22<-commodity_export[rev(order(commodity_export$`2021-2022`)),]
Top10.commodity_export_2021_22<-sorted_export_data21.22[1:10,]

#View(Top10.commodity_export_2021_22)
commodity.2021.22<-c("MINERAL,Crude Oil",
                     "Natural/Cultered Pearls",
                     "Nuc lear Reactors,Mechanical Appliances.",
                     "Iron and Steel",
                     "Organic Chemicals",
                     "Electrical Machinary &Equipments",
                     "VEHICLES PARTS & ACCESSORIES",
                     "PHARMACEUTICAL PRODUCTS  ",
                     "CEREALS",
                     "COTTON")


#Plotting top 10 commodity wise export for Fy2021-22. 
p1 <- ggplot(Top10.commodity_export_2021_22, aes(x = reorder(HSCode, -`2021-2022`), y = `2021-2022`/1000, fill = Commodity)) +
  geom_bar(stat = "identity") +
  ylim(0,100)+
  scale_fill_manual(values = c( "green", "blue", "orange", "purple", "pink","brown", "cyan", "yellow","magenta", "gold"))+
  labs(title = "Top 10 Exported commodities of 2021-22", x = "commodity", y = "USD billion  ") +
  geom_text(aes(label = round(`2021-2022`/1000,digits=2)), vjust = -0.8,size=3)+
  scale_x_discrete(labels = commodity.2021.22)

p1 <- p1 +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1, size = 7,face="bold"))
  

#sorted based on 2022-23 india's export.
sorted_export_data22.23<-commodity_export[rev(order(commodity_export$`2022-2023`)),]
Top10.commodity_export_2022_23<-sorted_export_data22.23[1:10,]
#View(Top10.commodity_export_2022_23)
commodity.2022.23<-c("Mineral,Crude Oil",
                     "Natural/Cultered Pearls",
                     "Electrical Machinary &Equipments",
                     "Nuclear Reactors,Machinary",
                     "ORGANIC CHEMICALS ",
                     "VEHICLES PARTS & ACCESSORIES",
                     "PHARMACEUTICAL PRODUCTS ",
                     "CEREALS",
                     "IRON AND STEEL",
                     "IRON OR STEEL ")

#Plotting top 10 commodity wise export for Fy2022-23.

p2 <- ggplot(Top10.commodity_export_2022_23, aes(x = reorder(HSCode, -`2022-2023`), y = `2022-2023`/1000, fill = Commodity)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values =c("red", "green", "orange", "purple", "pink", "brown", "cyan", "yellow", "magenta", "gold")) +
  labs(title = "Top 10 Exported commodities of 2022-23", x = "commodity", y = "USD billion  ") +
  geom_text(aes(label = round(`2022-2023`/1000,digits=2)), vjust = -0.8,size=3)+
  scale_x_discrete(labels = commodity.2022.23)

p2 <- p2 +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1, size = 7,face="bold"))
  # Create a single page with facets (one graph for each unique value)
  
# two export plots in single page.
ggarrange(p1,p2,ncol=2)

#sorting data on growth rate compared to previous year i.e data of high growth export commodities.

High_growth_export<-commodity_export[rev(order(commodity_export$`%Growth`)),]
View(High_growth_export)
Top20.High_growth_export<-High_growth_export[1:15,]
#View(Top20.High_growth_export)
export.commoditynames<-c(
  "ART PIECES & ANTIQUES",
  "WOOD Pulp MATERIAL",
  "NICKEL",
  "ANIMAL FODDER",
  "FERTILISERS",
  "MISCELLANEOUS GOODS",
  "PROJECT GOODS",
  "Mineral,Crude Oil",
  "Electrical Equipments",
  "EXPLOSIVES PYROTECHNIC PRODUCTS",
  "ANIMAL,VEGETABLE FATS AND OILS",
  "ZINC ",
  "TOBACCO&MANUFACTURED SUBSTITUTES",
  "EDIBLE VEGETABLES&CERTAIN ROOTS",
  "WOOL,COARSE ANIMAL HAIR"
)
#Top20.High_growth_export commodities plot.
p3<-ggplot(Top20.High_growth_export, aes(x = reorder(HSCode, -`%Growth`), y = `%Growth`, fill = Commodity)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 15 High growth Export commodities", x = "Commodity", y = "% Growth  ") +
  scale_x_discrete(labels = export.commoditynames )+
  theme(legend.position = "none",axis.text.x = element_text(angle =45,size=6,hjust=1,face="bold"))+
  geom_text(aes(label=`%Growth`),vjust=-.5,size=4)
  

print(p3)


```

Next we have high growth export commodities.Here we can see highest increase in export of commodity compared to previous year.

Where Works of art pieces&antiques,Pulp of wood/Fibrous cellulosic material,nickel,prepared animal fodder and fertilisers holds the top 5 spot .

Commodity wise Import Analysis:

```{r}
#Feather, Flowers & Hair Goods:PREPARED FEATHERS&ARTIFICIAL FLOWERS;ARTICLES OF HUMAN HAIR
#Mobility and Accessories:UMBRELLAS,WALKING-STICKS,SEAT-STICKS,WHIPS etc
  
#Import Analysis.
#commodity_import<-read_excel("C:/Users/Admin/Desktop/EDA/EDA_DATA_Main.xlsx",sheet = "CommoditywiseImport")

#View(commodity_import)

sorted_import_data21.22<-commodity_import[rev(order(commodity_import$`2021-2022`)),]
Top10.commodity_import_2021_22<-sorted_import_data21.22[1:10,]
#View(Top10.commodity_import_2021_22)

#Top10.commodity_import_2021_22 names
import_commodity.2021.22 <- c(
  "Crude Oil,Mineral Waxes",
  "NATURAL/CULTURED PEARLS",
  "Electrical Equipments",
  "NUCLEAR REACTORS,MECHANICAL APPLIANCES",
  "ORGANIC CHEMICALS",
  "PLASTIC",
  "PREPARED EDIBLE FATS",
  "FERTILISERS",
  "IRON AND STEEL",
  "MEDICAL,SURGICAL INST& APPARATUS"
)
#Top10.commodity_import_2021_22 plot
p4<-ggplot(Top10.commodity_import_2021_22, aes(x = reorder(Commodity, -`2021-2022`), y = `2021-2022`/1000, fill = Commodity)) +
  geom_bar(stat = "identity") +
  ylim(0,300)+
  scale_fill_manual(values = c( "green", "blue", "orange", "purple", "pink","brown", "cyan","navy", "yellow","magenta"))+
  labs(title = "Top 10 Imported commodities of 2021-22", x = "Commodity", y = "USD billion") +
  geom_text(aes(label = round(`2021-2022`/1000,digits=2)), vjust = -1,size=3)+
  scale_x_discrete(labels = import_commodity.2021.22)+
  theme(legend.position = "none",axis.text.x = element_text(angle = 45,size=6,hjust=1,face = "bold") )

print(p4)  

#Sorting data based on top imported commodities of 2022-23.
sorted_import_data22.23<-commodity_import[rev(order(commodity_import$`2022-2023`)),]
Top10.commodity_import_2022_23<-sorted_import_data22.23[1:10,]
#View(Top10.commodity_import_2022_23)

import_commodity.2022.23 <- c(
  "Crude Oil,Mineral Waxes",
  "NATURAL/CULTURED PEARLS",
  "Electrical Equipments",
  "NUCLEAR REACTORS,MECHANICAL APPLIANCES",
  "ORGANIC CHEMICALS",
  "PLASTIC",
  "EDIBLE FATS",
  "IRON AND STEEL",
  "FERTILISERS",
  "INORGANIC CHEMICALS"
)
#INORGANIC CHEMICALS;RARE-EARTH METALS:
#Top10.commodity_import_2022_23 plot
p5<-ggplot(Top10.commodity_import_2022_23, aes(x = reorder(Commodity, -`2022-2023`), y = `2022-2023`/1000, fill = Commodity)) +
  geom_bar(stat = "identity") +
  ylim(0,300)+
  scale_fill_manual(values = c( "green", "blue", "orange","red", "purple", "pink","brown", "cyan","yellow","magenta", "gold"))+
  labs(title = "Top 10 Imported commodities of 2022-23", x = "Commodity", y = "USD billion ") +
  geom_text(aes(label = round(`2022-2023`/1000,digits=2)), vjust = -1,size=3)+
  scale_x_discrete(labels = import_commodity.2022.23)+
  theme(legend.position = "none",axis.text.x = element_text(angle = 45,size=6,hjust=1,face="bold") )

print(p5)

#Multipleplot in single page
ggarrange(p5,p4,ncol=2)

################################################
#High growth import commodity analysis.
High_growth_import<-commodity_import[rev(order(commodity_import$`%Growth`)),]
#View(High_growth_import)
Top15.High_growth_import<-High_growth_import[1:15,]
#View(Top15.High_growth_import)


import.commoditynames<-c(
  "CEREALS",
  "COTTON",
  "WORKS OF ART PIECES &ANTIQUES",
  "AIRCRAFT, SPACECRAFT &PARTS",
  "SILK",
  "Mobility and Accessories",
  "SHIPS,BOATS &FLOATING STRUCTURES",
  "Feather, Flowers & Hair Goods",
  "DAIRY PRODUCE,NATURAL HONEY;",
  "GUMS,RESINS,OTHER SAPS",
  "Meat & Offal",
  "PAPER&ARTICLES OF PAPER PULP",
  "Sugar & Confectionery",
  "FOOTWEAR, GAITERS etc",
  "CLOTHING ACCESSORIES"

)


p6<-ggplot(Top15.High_growth_import, aes(x = reorder(Commodity, -`%Growth`), y = `%Growth`, fill = Commodity)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 15 High growth Import commodities", x = "Commodity", y = "% Growth  ") +
  geom_text(aes(label=`%Growth`),vjust=0)+
  scale_x_discrete(labels = import.commoditynames )+
  theme(legend.position = "none",axis.text.x = element_text(angle =45,size=6,hjust=1,face="bold"))

print(p6)

```

From this plot we can see that top 10 Imported commodities by India in both FY2021-22 &FY2022-23 where Mineral fuel,Natural /Cultured pearls and Electrical& Machinary Equipments holds the top 3 spot in both FY2021-22 and FY2022-23.

For high growth Import Commodities we can see Cereals,Cotton &Works of Antique pieces holds the top 3 spot.

Data Source:<https://commerce.gov.in/trade-statistics/>
